International Relations are a Social Network:\\ A Latent Network Approach for Global Politics

### 2017-10-20 paper/4_app.tex
okay, more app changes.

% % SM to MW: hmmm we should talk about the utility of this.
% see fig gibler_srmvc.pdf in the paper dir
% \begin{figure}
% 	\caption{}
% 	\includegraphics[width=\textwidth]{gibler_srmvc.pdf}
% 	\label{fig:gibler:dyadtriad}
% \end{figure}
% \FloatBarrier

@@

Fourth, it is useful to suggest that a lot of what is \textit{known} about international relations based on studies of dyadic data should be taken
with a grain of salt, until the interdependencies are taken into account.

>>>>

% MDW to SM:  yeah, Rose has so many variables that the network effects aren't that strong.
% Maybe we should mention this. If you put in a gazillion variables you might be okay.
% SM to MW: hmmm we should talk about the utility of this.
% see fig gibler_srmvc.pdf in the paper dir
% \begin{figure}
% 	\caption{}
% 	\includegraphics[width=\textwidth]{gibler_srmvc.pdf}
% 	\label{fig:gibler:dyadtriad}
% \end{figure}
% \FloatBarrier

@@

Fourth, it is useful to suggest that a lot of what is \textit{known} about international relations based on studies of dyadic data should be taken
with a grain of salt, and awaits a reassessment using methods that do not rely on an assumption that all the dyads are
independent and identically distributed.
